# A Plot Example

`knitr` is not well suited for serving dynamic content over an
application container as it does not allow us to set a working
directory (we fix it within our custom `raknit` method).

Then, there is another issue that all the by-products which are
created during the `knit` process are not available to the callsite,
such as images. We need to return a single, standalone HTML file as
output here.

In the following, we will use hack to generate plain vanilla R plots
and embed them into the page using *data* links.

## Step 1: Run the business logic and create the plot

This is where you do your analysis or business logic and generate the
plot. There are three important tweaks:

1. Define and remember the chunk name (We will use `MY-FIRST-CHUNK`).
2. Add `include=FALSE` as we do not want anything to be added to the document from this chunk.
3. Assign the return value of the plot function call to a dummy symbol (we won't use it).

Let's do it. Note that we won't attempt to read the image files in
this chunk as they won't be ready until the chunk is entirely
processed.

    ```{r "MY-FIRST-CHUNK", include=FALSE}`r ''`
    ## Let's create a first plot:
    .dummySymbol1 <- plot(1:10)

    ## And create another plot to demonstrate image file names:
    .dummySymbol2 <- plot(1:10, type="l")
    ```

```{r "MY-FIRST-CHUNK", include=FALSE}
## Let's create a first plot:
.dummySymbol1 <- plot(1:10)

## And create another plot to demonstrate image file names:
.dummySymbol2 <- plot(1:10, type="l")
```

By now, we have two files created in the current working directory:

1. `figure/MY-FIRST-CHUNK-1.png`
2. `figure/MY-FIRST-CHUNK-2.png`

Note the counter appended to the chunk name on each file name (1, 2, ...).

## Step 2: Create `<img>` tags

Let's generate image tags:

```{r}
## Read in the two image files:
file1 <- base64enc::base64encode("figure/MY-FIRST-CHUNK-1.png")
file2 <- base64enc::base64encode("figure/MY-FIRST-CHUNK-2.png")

## Let's generate the img tags:
img1 <- sprintf('<img src="data:image/png;base64,%s"/>', file1)
img2 <- sprintf('<img src="data:image/png;base64,%s"/>', file2)
```

## Step 3: Output image tags.

We will now use inline style to print our image tags. And that would
be all. **Note that the output is a standalone HTML document which can
be serialised and passed to various Internet services.**

    `r '\x60r img1'``

`r img1`

    `r '\x60r img2'``

`r img2`
